Developing model Hamiltonians for single and bilayer graphene using density matrix downfolding

### 2019-09-22 draft.tex
updated a line;

An important result from this study would be an accurate evaluation of $V(r)$ directly from \textit{ab initio} simulations.
This result would be able to validate commonly used models for the spatial dependence, like the Ohno form \cite{Ohno1964}.
It will also help develop understanding of interaction effects in graphene which depend on the details of $V(r)$, like edge magentism \cite{PhysRevB.95.195420} and non-local electrodynamics \cite{PhysRevB.90.045137}.
Additionally, by introducing displacement dependent parameters, one can determine whether phonons in graphene serve to simply renormalize interactions, or drastically alter them.
This determination is integral to understanding effects of strain on electronic properties as seen in experiment \cite{Naumis_2017}.

>>>>

An important result from this study would be an accurate evaluation of $V(r)$ directly from \textit{ab initio} simulations.
This result would be able to validate commonly used models for the spatial dependence, like the Ohno form \cite{Ohno1964}.
It will also help develop understanding of interaction effects in graphene which depend on the details of $V(r)$, like edge magentism \cite{PhysRevB.95.195420} and non-local electrodynamics \cite{PhysRevB.90.045137}.
Additionally, by introducing displacement dependent parameters, one can determine how phonons affect the effective electronic couplings in graphene.
This determination is integral to understanding effects of strain on electronic properties as seen in experiment \cite{Naumis_2017}.
